%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author:
% Satyam Goyal
%
% REFERENCE-
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\useunder{\uline}{\ulined}{}%
\DeclareUrlCommand{\bulurl}{\def\UrlFont{\ttfamily\color{blue}\ulined}}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Satyam}{Goyal}{
\href{https://www.linkedin.com/in/satyu26/}{{\faLinkedinSquare}{ satyu26}} |  \href{mailto:goyalsatyam8@gmail.com}{\faEnvelope{ goyalsatyam8@gmail.com}} | +91-7550264699 | \href{https://satyamgoyal.social}{satyamgoyal.social} | \href{https://github.com/SatYu26}{{\faGithub}{ SatYu26}}
}
\vspace{-5pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.43\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Bachelor of Technology}
\descript{SRM IST, Chennai, IN | CGPA - 8.76}
\location{June 2018 - June 2022}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{5pt}
\section{Skills}
\subsection{Programming}
\location{Language:}
\textbullet{}  Python \textbullet{} NodeJs \textbullet{} JavaScript \textbullet {} Java \textbullet{} C  \textbullet{} Dart \\
\location{Frameworks:}
\textbullet{} Express \textbullet{} React \textbullet{} Flutter \textbullet{} MERN Stack\\
\location{Database:}
MongoDB \textbullet{} Firebase Database \textbullet{} MySQL\\
\location{Platform and Tools:}
\textbullet{} Docker \textbullet{} Kubernetes \textbullet{} Git \textbullet{} Heroku \textbullet{} Firebase\\
\location{Others:}
\textbullet{} Data Structures \textbullet{} Algorithms \textbullet{} Selenium\\ \textbullet{} OpenCV \textbullet{} Machine Learning \textbullet{} Data Analysis\\ \textbullet{} TensorFlow \textbullet{} Googling\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{5pt}
\section{Links} 
Github:// \href{https://github.com/SatYu26}{\faGithub{  \bulurl{SatYu26}}} \ \ \ \ \
LinkedIn://  \href{https://www.linkedin.com/in/satyu26/}{\faLinkedinSquare{  \bulurl{satyu26}}} \\
LeetCode://  \href{https://leetcode.com/satyu/}{\bulurl{satyu}} \ \ \ \ \
Twitter://  \href{https://twitter.com/SatyuGoyal}{\bulurl{SatyuGoyal}}\\
Portfolio:// \href{https://satyamgoyal.social/}{\bulurl{satyamgoyal.social}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{5pt}
\section{Activities}
\runsubsection{Open Source}
\location{\href{https://github.com/SatYu26\#user-activity-overview}{\faGithub} \href{https://github.com/SatYu26\#user-activity-overview}{\bulurl{contributions}}}
\vspace{\topsep}
\begin{tightemize}
\item \href{https://github.com/flutter/samples/issues/667}{\bulurl{Flutter:}} Created Flutter-based Desktop Software and Added Google and Unsplash term links to it.
\item \href{https://github.com/Algo-Phantoms/Algo-ScriptML/pull/11}{\bulurl{
AlgoPhantoms:}} Scripted K-Means algorithm and enhanced the code usability and readability.
\item \href{https://github.com/Opentek-Org/opentek/pull/138}{\bulurl{
Opentek-Org:}} Updated and Refactored the Main website footer section with latest content.
\end{tightemize}


\runsubsection{GirlScript Summer of Code} \location{Feb 2021 - May 2021}
\begin{tightemize}
\item Participated in GSSoC and made many open-source contributions on many projects for 4 months.
\end{tightemize}


\runsubsection{Technical Lead} \location{June 2019 - July 2021}
\begin{tightemize}
\item Lead of Technical Domain in DSC Campus club by Google Developers and GFG Campus club.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{5pt}
\section{Achievements} 
\vspace{\topsep}
\begin{tightemize}
\item LeetCode - Solved more than 600 problems and participated in many contests on LeetCode and achieved a 3-star.\\
\item Hosted a 2 hours Hands On Workshop on "Understanding Open CV and Gestures Control Car Racing Game".\\
\item Became Microsoft Learn Student Ambassador and achieved Beta rank.\\
\item Part of top 7 teams in MozoHack 2021.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.56\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{HighRadius}
\descript{| Full Stack Intern}
\location{June 2021 – Aug 2021}
\vspace{\topsep}
\begin{tightemize}
\item Built an AI-enabled FinTech B2B Invoice Management Application, using React.js and Machine Learning.
\item Designed a Client-side Dashboard and connected its database with the ML model to fetch the correct prediction of the output.
\item Built a Random Forest and XG Boost Regression Model for Predicting the payment date of the invoice with an accuracy of 89\%.
\end{tightemize}
\ \ \ \ \ \ \location{Python, Node.js, React, Express, MySQL}
\sectionsep

\runsubsection{Crediwatch}
\descript{| Software Engineer Intern}
\location{Aug 2021 - Oct 2021}
\begin{tightemize}
\item Created an API for updating the database using Python and MongoDB and Reduced the data update time significantly.
\item Created a data gathering bot to collect contact informations and relevant data of Influencers from LinkedIn for Lead Generation.
\item Written web scraper with automated switching between pages and dynamic filtering of data on single page website.
\item Created an API to scrap and manage Legal data for the company from the Udyog Adhaar website.
\item Refactoring of Scripts to make Data Management more efficient. \ \ \ \ \ \ \ \ 
\end{tightemize}
\ \ \ \ \ \ \location{Python, Express, Node.js, MongoDB, Postgres, Bash}
\sectionsep

\runsubsection{Robic Rufarm}
\descript{| Software Engineer Intern}
\location{Apr 2020 – Jun 2020}
\begin{tightemize}
\item Designed and developed a web application and an Android application from scratch to monitor and interact with the Aerator system in the aquaculture farms using Flutter.
\item Reduced App response time in app by 32\% by implementing Asynchronous I/O with Firebase Database.
\item Managed to increase the yield by 10\% in aquaculture farms.
\end{tightemize}
\ \ \ \ \ \ \location{React, Node.js, Flutter, Dart, Firebase}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{5pt}
\section{Projects}
\runsubsection{Flash Type} \href{https://satyu26.github.io/Flash-Type/}{\faGithub{  \bulurl{LINK}}}
\descript{|  Web Application}
\begin{tightemize}
\item A typing speed tester to check multiple parameters such as Words per Minute and accuracy and share it on multiple platforms.
\end{tightemize}
\ \ \ \ \ \ \location{React, Redux}
\sectionsep

\runsubsection{User Auth Manager} \href{https://github.com/SatYu26/User-Auth-Management-System}{\faGithub{  \bulurl{LINK}}}
\descript{|  Rest API}
\begin{tightemize}
\item A system to Get the data of new user when they Sign-Up as well as check when the user is doing Sign-In if the user is already available and allow the user to sign-in successfully.
\end{tightemize}
\ \ \ \ \ \ \location{Node.js, Express}
\sectionsep

\runsubsection{Store Filter}
\href{https://github.com/SatYu26/StoreAPI}{\faGithub{  \bulurl{LINK}}}
\descript{|  Rest API}
\begin{tightemize}
\item A complete Filter system for managing E-Commerce website. This API contains various types of filter such as Sort, Fields, Limit and many more.
\end{tightemize}
\ \ \ \ \ \ \location{Node.js, Express, MongoDB}
\sectionsep

\runsubsection{Mask Recognition} \href{https://github.com/SatYu26/2021-Solution-Challenge-Submission}{\faGithub{  \bulurl{LINK}}}
\descript{| ML \& Android App}
\begin{tightemize}
\item App to detect face masks using smartphone in real-time.
\end{tightemize}
\ \ \ \ \ \ \location{Python, Keras, Tensorflow, Flutter, Android Studio}
\sectionsep

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

\end{minipage} 
\end{document}
